Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-09-18 date/paper.tex
Updates from Overleaf

\documentclass[]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath}
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{multirow}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or returns data and the amount of external data that cloned fragments use. We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
\end{abstract}

@@

\subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
We define the following characteristics of the extracted method and/or the call:
\begin{itemize}
\item \textbf{Tokens}: The number of tokens in the body of the method.
\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
\item \textbf{Returns}: Whether the method calls return, declare, assign or doesn't use any data from the extracted method.
\item \textbf{Parameters}: The number of parameters the extracted method has.
\end{itemize}
We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.

@@

\subsubsection{Relation}
We tested to what extent the relation between clone instances in a clone class (see Sec.~\ref{sec:relation}) has an influence on the maintainability of refactored clones.

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{references}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath}
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{multirow}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use. We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
\end{abstract}

@@

\subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
We define the following characteristics of the extracted method and/or the call:
\begin{itemize}
\item \textbf{Tokens}: The number of tokens in the body of the method.
\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
\item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
\item \textbf{Parameters}: The number of parameters the extracted method has.
\end{itemize}
We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.

@@

\subsubsection{Relation}
Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).

\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

@@

\subsubsection{Return Value}
Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.

\begin{table*}
\centering
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
\rowcolor[HTML]{FFCCC9}
Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
\end{tabular}
\caption{Average metric values for refactorings of clone classes with the specified return category}
\label{tab:return}
\end{table*}

The displayed return categories are ordered by their scores. Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability. When the result of the call to the extracted method is directly returned, the maintainability score is the highest. When no value is returned, the maintainability score is the lowest. The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.

@@

\bibliography{references}
